Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

The part of the paper from now until the appendix will be devoted to proving the above lemma. This is the most challenging step in settling the general $k$-SJ problem optimally.

@@

>>>>

The part of the paper from this point onwards until the appendix will be devoted to proving the above lemma. This is the most challenging step in settling the general $k$-SJ problem optimally, as we will see in Appendix~\ref{app:kSJ}, where we will prove Theorems~\ref{thm:main-recur} and \ref{thm:main-alg} based on Lemma~\ref{lmm:hv}.

@@

\section{Solving the $k$-SJ Problem} \label{app:ksj}
